invivoPKfit analysis of CvTdb data

### 2023-01-23 Working Rmds/MainAnalysis.Rmd
Added several functions to evaluate fits.
preprocess_data() now retains CvTdb series and study IDs.

Updated documentation for several functions.

```{r}
names_list <- list(
  "Compound_Dosed" = "studies.test_substance_name_original",
  "DTXSID_Dosed" = "chemicals_dosed.dsstox_substance_id",
  "CAS_Dosed" = "chemicals_dosed.dsstox_casrn",
  "Compound_Analyzed" = "series.analyte_name_original",
  "DTXSID_Analyzed" = "chemicals_analyzed.dsstox_substance_id",
  "CAS_Analyzed" = "chemicals_analyzed.dsstox_casrn",
  "Reference" = "documents_reference.id",
  "Extraction" = "documents_extraction.id",
  "Species" = "subjects.species",
  "Weight" ="subjects.weight_kg",
  "Weight.Units" = NULL,
  "Dose" = "studies.dose_level_normalized_corrected", #note that dose levels were corrected in pulling_oral_iv_data_cvtdb.Rmd
  "Dose.Units" = NULL,
  "Time" = "conc_time_values.time_hr",
  "Time.Units" = NULL,
  "Media" = "series.conc_medium_normalized",
  "Value" = "conc_time_values.conc", #already normalized to mg/L units in CvTdb
  "Value.Units" = NULL,
  "Route" = "studies.administration_route_normalized",
  "LOQ" = "series.loq_normalized", #note that LOQs were normalized to mg/L units in pulling_oral_iv_data_cvtdb.Rmd
  "Subject" = "subjects.id",
  "N_Subjects" = "series.n_subjects_in_series",
  "Value_SD" = "conc_time_values.conc_sd_normalized" #note that SDs were normalized to mg/L units in pulling_oral_iv_data_cvtdb.Rmd
  )
```

>>>>

```{r}
names_list <- list(
  "Compound_Dosed" = "studies.test_substance_name_original",
  "DTXSID_Dosed" = "chemicals_dosed.dsstox_substance_id",
  "CAS_Dosed" = "chemicals_dosed.dsstox_casrn",
  "Compound_Analyzed" = "series.analyte_name_original",
  "DTXSID_Analyzed" = "chemicals_analyzed.dsstox_substance_id",
  "CAS_Analyzed" = "chemicals_analyzed.dsstox_casrn",
  "Reference" = "documents_reference.id",
  "Extraction" = "documents_extraction.id",
  "Species" = "subjects.species",
  "Weight" ="subjects.weight_kg",
  "Weight.Units" = NULL,
  "Dose" = "studies.dose_level_normalized_corrected", #note that dose levels were corrected in pulling_oral_iv_data_cvtdb.Rmd
  "Dose.Units" = NULL,
  "Time" = "conc_time_values.time_hr",
  "Time.Units" = NULL,
  "Media" = "series.conc_medium_normalized",
  "Value" = "conc_time_values.conc", #already normalized to mg/L units in CvTdb
  "Value.Units" = NULL,
  "Route" = "studies.administration_route_normalized",
  "LOQ" = "series.loq_normalized", #note that LOQs were normalized to mg/L units in pulling_oral_iv_data_cvtdb.Rmd
  "Subject" = "subjects.id",
  "N_Subjects" = "series.n_subjects_in_series",
  "Value_SD" = "conc_time_values.conc_sd_normalized", #note that SDs were normalized to mg/L units in pulling_oral_iv_data_cvtdb.Rmd
  "Study_ID" = "studies.id",
  "Series_ID" = "series.id"
  )
```
